Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-12 paper_io_sim.tex
Add links to nighres examples

            Our fourth and final experiment (\textit{Exp Nighres})
            simulates the Nighres CRUISE cortical reconstruction workflow
            \tristan{describe data, and if the execution was single node or
            distributed.}

>>>>

            Our fourth and final experiment (\textit{Exp Nighres})
            simulates the Nighres CRUISE cortical reconstruction workflow, which consists 
            of four tasks. The first two tasks are skull stripping and MGDM segmentation, 
            which are in this Nighres example: 
            \url{https://nighres.readthedocs.io/en/latest/auto_examples/example_01_tissue_classification.html}. 
            The last two steps are region extraction and CRUISE cortical reconstruction 
            in this example: 
            \url{https://nighres.readthedocs.io/en/latest/auto_examples/example_02_cortical_depth_estimation.html}.
            \tristan{describe data, and if the execution was single node or
            distributed.}
